### 2024-03-25 mycv/subs/papers.tex
snapshot

@@

@@

  {Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}

>>>>

  {Jos\'{e} Victoria-Hern\'{a}ndez, \underline{Y. Jeong}$^*$, Dietmar Letzig}
  {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}

@@

  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
  {Jaeseong Lee, Dirk Steglich, \underline{Y. Jeong}$^*$}
  {Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}

@@

  {\href{https://doi.org/10.1016/j.msea.2023.145904}{Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}}
  {Materials Science and Engineering: A}
  {Vol. 890, 149504, 2024}
